Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-16 WSSSPE3/report/wg_appendix_industry_interaction.tex
minor wording changes

\subsection{Plan for Future Organization}
No concrete plans were made at this point. If community can rally behind, some momentum could be built. If you are interested post at \url{https://github.com/WSSSPE/meetings/issues/46}

@@

\subsection{Description of Funding Needed}
Concrete funding needs were not discussed in this working group but a general impression was a seed funding will motivate members of this group or others in community to launch a survey effort.

>>>>

\subsection{Plan for Future Organization}
No concrete plans have been made at this point. If the community can rally behind this topic, some momentum could be built. Those interested should post at \url{https://github.com/WSSSPE/meetings/issues/46}

@@

\subsection{Description of Funding Needed}
Concrete funding needs were not discussed in this working group but a general impression was that some seed funding would motivate members of this group or others in community to launch a survey effort.
